Untitled

### 2017-07-20 PaperCode.Rmd
Exclude Other
Set up the code to be able to bootstrap excluding the "other" type of ptoperty

@@

>>>>

#ExO excluding Other
#A only A type sales
#B only Btype sales

@@

#Repeat excluding all the properties classed as other

BootStrapRESExO <-LoadAddDistribCompare("BootStrapRESExO.rds", 
                                         PropertyTypes = c("D", "S", "T", "F"))

BootStrapRESExOA <-LoadAddDistribCompare("BootStrapRESExOA.rds", type = "A", 
                                         PropertyTypes = c("D", "S", "T", "F"))

BootStrapRESExOB <-LoadAddDistribCompare("BootStrapRESExOB.rds", type = "B", 
                                         PropertyTypes = c("D", "S", "T", "F"))
